Grow with the flow: faster growth is associated with more variable precipitation in a perennial herb

### 2016-10-06 ms/ms.Rnw
Worked on analysis and ms

  # The path to the ms directory may need to be changed for different users
  # Manuscript files
  # pathMS <- "~/Google Drive/CardLocalAdaptation/ms" # Chris' MacBook
  # pathMS <- "~/Documents/CardAdapt/ms" # Chris' Linux laptop
  pathMS <- "/Users/amylauren/Desktop/CardAdapt/ms" # Amy's desktop

@@

# Read in spatially-averaged (10 km buffer) for 16 focal populations
load(paste(pathDat, "/focClimSA.RData", sep = ""))

@@

  # Intrinsic photosynthetic rate
  # = residuals of Conductance - Photosynthesis regression
  # Removed one outlier (may change if data are rearranged!)
	mm <- lmer(resPhoto ~ PopID * TempTrt * WaterTrt + (1|Family) + (1|Block),
    data = subset(master, !is.na(master$Photo))[-52, ])
	fitIntrnPhoto <- step(mm, reduce.random = F)

@@

\paragraph{Mortality}
We assayed mortality during twice-weekly growth measurements. We could not get GLMM with Family effects to converge, so we used GLM with a quasibinomial error structure and assessed signifiance using Type 2 Analysis of Deviance with the R package \pkg{car}.

@@

  fitMort <- glm(DiedFromStress ~ PopID * TempTrt * WaterTrt,
    data = subset(master, !is.na(master$DiedFromStress)), 
    family = "quasibinomial")

  fitMort <- glmer(DiedFromStress ~ PopID * TempTrt * WaterTrt + (1|Family) +
  								 (1|Block), data = subset(master, !is.na(master$DiedFromStress)), family = "binomial")
  Anova(fitMort, type = 2)
@

@@

  # Figure of variable importance for latitude
  pdf(paste(pathFig, "/Figure_clim2lat_imp.pdf", sep = ""), 4, 5)
  par(mar = c(5, 6, 1, 1))
  plot(0, 0, type = "n", xlim = c(0, ceiling(vsurfLat$ord.imp$x)[1]), 
		ylim = c(1, length(vsurfLat$varselect.pred)), axes = F, frame.plot = T, 
		xlab = "", ylab = "")
	title(xlab = "Climate-Latitude\nImportance", line = 4, cex.lab = 1.5)
  for (i in 1:length(vsurfLat$varselect.pred)) 
  {
     lines(x = c(-1, length(vsurfLat$varselect.pred)), y = c(i, i), col = "grey")
  }
  points(vsurfLat$ord.imp$x[1:length(vsurfLat$varselect.pred)], 
    length(vsurfLat$varselect.pred):1, pch = 21, col = "black", bg = "white", cex = 1.5)
	# mtext(climVars[vsurfLat$varselect.pred], side = 2, 
    # at = length(vsurfLat$varselect.pred):1, las = 1, line = 1)
	axis(1, lwd = 0, lwd.ticks = 1)
	dev.off()

@@

   \topcaption[ANOVA summary]{Summary of Population, Treatment, and Population $\times$ Treatment effects. We used different statistical modeling for the diverse traits assayed -- glm: generalized linear model using R \citep{R}; lmer: linear mixed model using the R package \pkg{lme4} \citep{Bates_etal_2014}; survreg: survival regression using the R package \pkg{survival} \citep{Therneau_2015}. Note that temperature and water treatments were imposed after germination, hence are not application to this trait. Key to statistical significance: *$P < 0.05$; ** $P < 0.01$; *** $P < 0.001$}

@@

    Statistical model              & survreg     & lmer           & lmer            & lmer           & lmer          & glm \\

>>>>

  # The path to the ms directory may need to be changed for different users
  # Manuscript files
  pathMS <- "~/Google Drive/CardAdapt/ms" # Chris' MacBook Air
  # pathMS <- "~/Documents/CardAdapt/ms" # Chris' Linux laptop
  # pathMS <- "/Users/amylauren/Desktop/CardAdapt/ms" # Amy's desktop

@@

# Read in spatially-averaged (100 km buffer) for 16 focal populations
load(paste(pathDat, "/focClimSA.RData", sep = ""))

@@

  # Intrinsic photosynthetic rate
  # = residuals of Conductance - Photosynthesis regression
  # Removed one outlier (may change if data are rearranged!)
	mm <- lmer(resPhoto ~ PopID * TempTrt * WaterTrt + (1|Family) + (1|Block),
    data = subset(master, !is.na(master$Photo))[-52, ])
	fitIntrnPhoto <- step(mm, reduce.random = F) # only Pop

@@

\paragraph{Mortality}
We assayed mortality during twice-weekly growth measurements. We analyzed the probability of surviving until the end of the experiment as a function of population, treatment, and their interactions using a Generalized Linear Mixed Model (GLMM) assuming binomially distributed errors. As before, we included Family and Block as random factors. We assessed significance of fixed effects using Type 2 Analysis of Deviance with Wald \Chi$^2$ tests in the R package \pkg{car} \citep{Fox_Weisberg_2011}.

@@

	# Code for GLM (remove if satisfied with GLMER)
  # fitMort <- glm(DiedFromStress ~ PopID * TempTrt * WaterTrt,
  #  data = subset(master, !is.na(master$DiedFromStress)), 
  #  family = "quasibinomial")

  fitMort <- glmer(DiedFromStress ~ PopID * TempTrt * WaterTrt + (1|Family) +
  								 (1|Block), control = glmerControl(optimizer = "bobyqa"),
  								 data = subset(master, !is.na(master$DiedFromStress)), 
  								 family = "binomial")
  # Anova(fitMort, type = 2)
@

@@

  # Figure of variable importance for latitude
  pdf(paste(pathFig, "/Figure_clim2lat_imp.pdf", sep = ""), 4, 5)
  par(mar = c(5, 6, 1, 1))
  plot(0, 0, type = "n", xlim = c(0, ceiling(vsurfLat$imp.mean.dec)[1]), 
		ylim = c(1, length(vsurfLat$varselect.pred)), axes = F, frame.plot = T, 
		xlab = "", ylab = "")
	title(xlab = "Climate-Latitude\nImportance", line = 4, cex.lab = 1.5)
  for (i in 1:length(vsurfLat$varselect.pred)) 
  {
     lines(x = c(-1, length(vsurfLat$varselect.pred)), y = c(i, i), col = "grey")
  }
  points(vsurfLat$imp.mean.dec[1:length(vsurfLat$varselect.pred)], 
    length(vsurfLat$varselect.pred):1, pch = 21, col = "black", bg = "white", cex = 1.5)
	# mtext(climVars[vsurfLat$varselect.pred], side = 2, 
    # at = length(vsurfLat$varselect.pred):1, las = 1, line = 1)
	axis(1, lwd = 0, lwd.ticks = 1)
	dev.off()

@@

   \topcaption[ANOVA summary]{Summary of Population, Treatment, and Population $\times$ Treatment effects. We used different statistical modeling for the diverse traits assayed -- glmer: generalized linear mixed model using the R package \pkg{lme4} \citep{Bates_etal_2014}; lmer: linear mixed model using the R package \pkg{lme4} \citep{Bates_etal_2014}; survreg: survival regression using the R package \pkg{survival} \citep{Therneau_2015}. Note that temperature and water treatments were imposed after germination, hence are not application to this trait. Key to statistical significance: *$P < 0.05$; ** $P < 0.01$; *** $P < 0.001$}

@@

    Statistical model              & survreg     & lmer           & lmer            & lmer           & lmer          & glmer \\
